\section{Introduction}

\subsection{Problem Statement}
\begin{frame}{Problem Statement}
	In this project we aim to enhance online fashion retail by developing an AI-based clothing recommender and an AR-powered virtual try-on towards reducing uncertainty and high return rates amongst consumers.
\end{frame}

\subsection{Motivation}
\begin{frame}{Motivation}
	\begin{enumerate}
		\item Online shoppers face an overwhelming array of clothing choices, often leading to hesitation and indecision.
		\item The inability to try on garments before purchase has long been a pain point for consumers.
		\item The issue of high return rates in e-commerce, particularly in the fashion sector, has far-reaching environmental consequences.
	\end{enumerate}
\end{frame}

\subsection{Literature Review}
\newcommand{\checkif}[1]{
	\ifthenelse{\equal{#1}{Y}}{\checkmark}{}
}
\newcommand{\rsrow}[8]{
	\citeauthor{#1} \cite{#1} & #2 &
	\checkif{#3} &
	\checkif{#4} &
	\checkif{#6} &
	\checkif{#8}
	\\ \hline
}

\newcommand{\commrow}[3]{
	#2 & \cite{#1} & #3 \\ \addlinespace
}
\begin{frame}[allowframebreaks]{Literature Review}
	A review of Fashion Recommendation Systems:
	{
		\tiny
		\renewcommand{\arraystretch}{1.15}
		\begin{xltabular}{\textwidth}{
			p{2.25cm} | X |
			>{\centering\arraybackslash}p{1cm} |
			>{\centering\arraybackslash}p{1.15cm} |
			>{\centering\arraybackslash}p{1.05cm} |
			>{\centering\arraybackslash}p{1.15cm}
		}
			\hline
				\textbf{Authors} &
				\textbf{Technique(s)} &
				\multicolumn{2}{c|}{\textbf{User Inputs}} &
				\multirow{2}{1.1cm}{\centering \textbf{Outfit Generation}} &
				\textbf{Personalized} \\
				& & Attributes & Interactions\footnotemark[1] & & \\
			\hline \hline
				\rsrow{DBLP:journals/eswa/MoZPW23}{
					Transformer $\rightarrow$ Transformer
				}{Y}{}{Y}{Y}{}{Y}
				\rsrow{10049142}{
					Contextual Attention Network
				}{}{}{Y}{Y}{}{}
				\rsrow{DBLP:journals/eswa/BalimO23}{
					CNN $\rightarrow$ LSTM + Transformer
				}{}{Y}{Y}{}{Y}{}
				\rsrow{9857004}{
					Triplet Network
				}{}{}{Y}{Y}{}{}
				\rsrow{9893574}{
					Bi-LSTM, GAN
				}{}{}{Y}{Y}{}{}
				\rsrow{9775146}{
					Bi-LSTM
				}{}{}{Y}{Y}{}{}
				\rsrow{DBLP:journals/tomccap/YangSFWDN21}{
					Representation Learning
				}{}{Y}{Y}{Y}{Y}{}
				\rsrow{DBLP:conf/iccvw/KimSMSSP21}{
					CNN + Projection Head
				}{}{}{Y}{Y}{}{}
				\rsrow{9156535}{
					CNN + Triplet Network
				}{}{}{Y}{Y}{}{}
				\rsrow{DBLP:conf/sigir/DongWSDN20}{
					Bi-LSTM
				}{}{}{Y}{Y}{}{}
				\rsrow{DBLP:journals/ijon/SunHWZP20}{
					LSTM + Triplet Network
				}{}{}{Y}{Y}{}{}
				\rsrow{9156794}{
					CNN $\rightarrow$ Joint Embedding
				}{Y}{}{Y}{Y}{Y}{Y}
				\rsrow{DBLP:conf/sigir/LiW0CXC20}{
					Heirarchical Graph Network
				}{}{}{Y}{Y}{}{}
				\rsrow{DBLP:journals/corr/abs-2005-06584}{
					Relational Network + VSE
				}{}{}{Y}{Y}{}{}
				\rsrow{DBLP:conf/kdd/ChenHXGGSLPZZ19}{
					BPR + CNN $\rightarrow$ Transformer
				}{}{Y}{Y}{Y}{}{Y}
				\rsrow{DBLP:conf/mm/SongHLCXN19}{
					CNN + TextCNN
				}{}{Y}{Y}{Y}{}{Y}
			\addlinespace
			\multicolumn{6}{l}{\textit{\footnotemark[1] Purchase data, comments, ratings, reviews}}
		\end{xltabular}
	}

	\pagebreak

	A review of Virtual Try-On systems:
	{
		\scriptsize
		\renewcommand{\arraystretch}{1.5}
		\begin{xltabular}{\textwidth}{
			p{2cm}
			p{2cm}
			X
		}
			\toprule
				\textbf{Technology} &
				\textbf{Works studied} &
				\textbf{Limitations} \\
			\midrule
				Image-based & 29 \cite{DBLP:conf/iccvw/AyushJCHK19, DBLP:conf/iccv/HanHHS19, DBLP:conf/iccvw/KuboISM19, DBLP:conf/iccvw/LeeLKCP19, DBLP:conf/iccv/YuWX19, DBLP:conf/iccvw/YildirimJVB19, minar2020cp, DBLP:conf/eccv/IssenhuthMC20, minar20203d, DBLP:conf/cvpr/LiCZL21, DBLP:journals/access/MinarTA21, DBLP:conf/cvpr/GeSGY0021, DBLP:conf/cvpr/ChoiPLC21, DBLP:conf/cvpr/GeSZG0021, DBLP:conf/iccv/ChenLHSC21, DBLP:conf/iccv/ChopraJHK21, DBLP:conf/iccv/CuiML21, DBLP:conf/cvpr/FenocchiMCBCC22, DBLP:conf/cvpr/FengMSGLLOZZ22, DBLP:conf/cvpr/HeSX22, DBLP:conf/cvpr/YangY022, DBLP:conf/eccv/BaiZLZY22, DBLP:conf/eccv/LeeGPCC22, DBLP:conf/wacv/FeleLPS22, DBLP:conf/nips/HuangLXKCL22, DBLP:conf/cvpr/ZhuYZRCS0K23, DBLP:journals/corr/abs-2304-02051, DBLP:conf/cvpr/YanGZX23, DBLP:conf/cvpr/XieHDZDZ0L23}
				& Limited interaction, lack of 360-degree view, limited assessment.
				\\
				Pose-guided & 17 \cite{DBLP:conf/cvpr/SongZLM19, DBLP:conf/iccv/AlbaharH19, DBLP:conf/cvpr/LiHL19, DBLP:journals/corr/abs-1906-07251, DBLP:conf/iccv/LiuPML0G19, DBLP:conf/ijcai/HuangXCWZWHD20, DBLP:conf/cvpr/MenMJML20, DBLP:journals/tip/LiZLLD20, DBLP:conf/cvpr/WangWFLZXZ20, DBLP:journals/tip/RenLLL20, DBLP:journals/corr/abs-2008-11898, DBLP:journals/corr/abs-2006-01435, DBLP:journals/tog/AlBaharLYSSH21, DBLP:journals/pami/ZhuHXSCB22, DBLP:conf/cvpr/DongZXZDZLLY22, DBLP:conf/eccv/ZhouYCSGL22, DBLP:conf/cvpr/FruhstuckSSMWL22}
				& Restricted by training on predefined poses, reliant on pose tracking performance.
				\\
				Multi-pose & 5 \cite{DBLP:conf/icip/HsiehCCSC19, DBLP:conf/iccv/DongLSWLZH019, DBLP:journals/access/ThaiMAW21, DBLP:journals/tmm/HuLZR22, du2023cf}
				& Complex to develop.
				\\
				Video & 3 \cite{DBLP:conf/wacv/KuppaJLLM21, DBLP:conf/mm/ZhongWTLW21, DBLP:conf/cvpr/JiangWYL22}
				& Data intensive.
				\\
				3D & 2 \cite{DBLP:conf/wacv/MajithiaPBGSS22, DBLP:conf/nips/SantestebanOTC22}
				& Mesh generation is complex, inaccurate meshes cause misalignment.
				\\
				AR & 9 \cite{DBLP:conf/ieeehpcs/JongM19, di2020comparative, hashmi2020augmented, baytar2020evaluating, shaw2020advanced, ali2021augmented, feng2021personalized, moriuchi2021engagement, DBLP:journals/sensors/BattistoniGRSVB22}
				& Limited environment adaptability.
				\\
			\bottomrule
		\end{xltabular}
	}

	\pagebreak

	A review of Commercial Virtual Try-On systems:
	{
		\scriptsize
		\newlength{\limwidth}
		\setlength{\limwidth}{5.75cm}
		\begin{xltabular}{\textwidth}{
			p{1.5cm}
			X
			p{\limwidth}
		}
			\toprule
				\textbf{Technology} &
				\textbf{Item type} &
				\textbf{Limitations} \\
			\midrule
				\textbf{2D} & Clothing \& Accessories & \multirow{3}{\limwidth}{\justifying AI-generated variations of garment try-on images are not true representations of a user trying on the garment.} \\
				& \cite{WalmartA, WalmartB, GoogleShopping} & \\
				& & \\
			\midrule
				\textbf{AR} & Clothing \& Accessories \cite{Snapchat} & \multirow{2}{\limwidth}{\justifying Most implementations only focus on accessories instead of actual clothing items.} \\
				& Clothing \cite{Zalando} & \\
				& Wrist Watches \cite{BaumeMercier} & \\
				& Eyewear \cite{WarbyParker} & \\
				& Makeup \cite{YTAR} & \\
				& Makeup \cite{LOreal} & \\
			\bottomrule
		\end{xltabular}
	}
\end{frame}

\subsection{Research Gaps}
\begin{frame}{Research Gaps}
	The following research gaps were identified from literature review:
	\begin{enumerate}
		\item Limited inclusion of body attributes or user interaction data into clothing recommendation systems.
		\item Limited work done on personalized clothing recommendation.
		\item Lack of robust and visually appealing AR implementations of virtual try-on.
		\item Lack of model/system deployment causing deficiency of online performance evaluation under real-world loads and constraints.
	\end{enumerate}
\end{frame}

\subsection{Objectives}
\begin{frame}{Objectives}
	This project has the following objectives:
	\begin{enumerate}
		\item Personalized clothing recommendation.
		\item Enhanced user engagement strategies.
		\item Increased consumer conversion rates.
		\item Reduction of return rates.
		\item Increased revenue for businesses.
		\item Data privacy and security compliance.
		\item Laying groundwork for future integration with personal AI assistants.
	\end{enumerate}
\end{frame}